si: code and prose exploring Spatial Interaction models

### 2022-04-22 README.qmd
Tweak readme
Former-commit-id: c6f5f113465bfe6929388bb3bbc8fedae03ec16f

---
# format: html
format: gfm
title: "si: code and prose exploring Spatial Interaction models"
bibliography: vignettes/references.bib
execute:
  cache: false
  fig.path: "man/figures/README-"
  message: false
---

@@

The goal of {si} is to provide a simple and flexible framework for developing spatial interaction models (SIMs), which estimate the amount of movement between spatial entities.

>>>>

---
# format: html
format: gfm
bibliography: vignettes/references.bib
execute:
  cache: false
  fig.path: "man/figures/README-"
  message: false
---

@@

The goal of {si} is to provide a simple, '[tidy](https://dplyr.tidyverse.org/)', and flexible framework for developing spatial interaction models (SIMs), which estimate the amount of movement between spatial entities.
